Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-06-13 paper/paper.Rmd
include example for custom resampling

### Group-level CV

@@

### Custom Resampling --- mlr3

>>>>

### Group-Level CV

@@

### Custom (fixed) Resampling --- mlr3

Support for user-defined partitioning strategies is built into \pkg{mlr3} directly since version FIXME.
Labelled as "Custom CV", users are able to supply an external factor vector with the same length as number of observations.
Alternatively to supplying an external factor vector, the name of a feature within the task can be used.

The following example is taken from `sperrorest::partition_factor()`.

FIXME: eval=TRUE when available upstream im mlr3

```{r custom-cv,  fig.cap="Environmental blocking using a single predictor.", out.width="50%", fig.pos="ht", eval=FALSE}
breaks <- quantile(task$data()$dem, seq(0, 1, length = 6))
zclass <- cut(task$data()$dem, breaks, include.lowest = TRUE)

resampling_custom = rsmp("custom_cv")
resampling_custom$instantiate(task, split = zclass)
```
